Rethinking Felony Disenfranchisement: The Case of New York City and Miami

### 2019-05-07 markdown/kmorris_thesis.Rmd
add individuals on parole as of 2017 election (was previously just incarcerated people)

---
title: "Rethinking Felony Disenfranchisement: The Case of New York City and Miami"
author: "Kevin Morris"
date: "April 22, 2019"
output:
  bookdown::pdf_document2:
    toc: no
    fig_caption: yes
bibliography: "../research/citations.bib"
link-citations: yes
---
<!-- --- -->
<!-- title: "Rethinking Felony Disenfranchisement: The Case of New York City and Miami" -->

@@

<!-- output: rticles::asa_article -->
<!-- --- -->
```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf"
                     )
library(scales)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(stargazer)
```
"There is no Negro problem. There is no Southern problem. There is no Northern problem. There is only an American problem"

@@

```{r citywide-map, echo = FALSE, fig.width = 5, fig.height = 5, fig.cap = "\\label{fig:citymap}Individuals Incarcerated in 2017 Who Voted Between 2007 and 2016", out.extra = '', fig.pos = "H", fig.align = "center"}
j <- readRDS("./output/city_map.RDS")
j
```
The spatial concentration of lost

>>>>

---
title: "Rethinking Felony Disenfranchisement: The Case of New York City and Miami"
author: "Kevin Morris"
date: "April 22, 2019"
output:
  bookdown::pdf_document2:
    toc: no
    fig_caption: yes
    latex_engine: xelatex
bibliography: "../research/citations.bib"
link-citations: yes
---
<!-- --- -->
<!-- title: "Rethinking Felony Disenfranchisement: The Case of New York City and Miami" -->

@@

<!-- output: rticles::asa_article -->
<!-- --- -->
```{r setup, echo = F, message = F, warning = F}
knitr::opts_knit$set(root.dir = "..", dev = "cairo_pdf"
                     )
library(scales)
library(tidyverse)
library(extrafont)
library(kableExtra)
library(stargazer)

```
"There is no Negro problem. There is no Southern problem. There is no Northern problem. There is only an American problem"

@@

```{r citywide-map, echo = FALSE, message = F, warning = F, fig.width = 5, fig.height = 5, fig.cap = "\\label{fig:citymap}Individuals Incarcerated in 2017 Who Voted Between 2007 and 2016", out.extra = '', fig.pos = "H", fig.align = "center"}
j <- readRDS("./output/city_map.RDS")
print(j)
```
The spatial concentration of lost
